Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-15 paper/paper1/ms.tex
Add HPF figure

Figure X shows

\authorcomment1{Add overplots of He and Ca II.}

\subsection{EW Uncertainty quantification with MCMC}
We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}. The model consists of a straight-line trend with a Gaussian absorption line.  It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.

We computed the equivalent width with the closed-form integral:

\begin{gather}
    W_\lambda=\frac{Aw}{m \mu + b}\cdot\sqrt{2\pi}
\end{gather}

Ultimately the MCMC method was highly accurate but imprecise, and was replaced in favor of \emph{data-driven} methods.

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figures/stellar_periodogram.png}
    \caption{Periodogram of solely the stellar variation of the flux. }
    \label{fig:stellar_periodogram}
\end{figure}

>>>>

Figure \ref{fig:HPF2022campaign} shows a zoom-in on the He 10830 region of interest.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT-P-67_2022_clean.png}
    \caption{HPF spectrum of HAT-P-67 around the spring 2022 campaign.  We see conspicuous absorption during and immediately preceding the transit, but not immediately after.  The continuum normalization indices are shown by the vertical blue shaded region and the region used for computing EW is shown in the faint gray vertical band.}
    \label{fig:HPF2022campaign}
\end{figure}

%\subsection{EW Uncertainty quantification with MCMC}
%We assessed the uncertainty in our equivalent fit Gaussian line profiles to the He 10830 line with \texttt{emcee} \citep{foreman13}. The model consists of a straight-line trend with a Gaussian absorption line.  It has five parameters: the straight-line trend slope $m$ and offset $b$, and the Gaussian amplitude $A$, center wavelength $\mu$, and width $w$.

@@
